DOpElib: Differential Equations\\ and Optimization Environment

### 2013-05-11 Examples/OPT/StatPDE/Example9/content.tex
Finished overhaul of OPT StatPDE examples. 7 and 8 are untested due to missing snopt

In this example we solve an optimization problem where 
the equations come from fluid-structure interaction (FSI). The idea
is to extend the steady FSI benchmark problem (FSI 1) to an optimization 
problem where the drag is minimized over the cylinder plus beam.

@@

Detailed description will follow later.

>>>>

\subsubsection{General program description}
In this example we solve an optimization problem where 
the equations come from fluid-structure interaction (FSI). The idea
is to extend the steady FSI benchmark problem (FSI 1, proposed by Hron/Turek) to an optimization 
problem where the drag is minimized over the cylinder and the beam.

@@

Detailed description will follow later. %TODO
